*Prochlorococcus marinus* responses to light and oxygen

### 2024-02-21 Code/Manuscript_O2.Rmd
added {.unnumbered} to all headings

## Detection of *Prochlorococcus* proteins across O~2~ and light niches in the ocean

@@

## *Prochlorococcus marinus* growth responses to photoperiod, PAR, spectral bands,  and O~2~

@@

### MED4 Clade HLI
The GAM model in Figure \@ref(fig:MED4GAM) shows MED4 growth in response to red (A) or blue (B) peak PAR and photoperiod across 2 imposed oxygen concentrations.  Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.69 d^-1^ contour line representing the
90^th^ percentile of maximum achieved growth rate.  Growth decreased with decreasing photoperiod and peak PAR.  Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR waas similar.  We again note the exclusion of MED4 from growth under 4 h photoperiod. Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods.

@@

# Acknowledgements
Jonah Sheinin assisted with growth of some cultures for protein analyses, while Carlie Barnhill assisted with code for import of multicultivator growth data files.

# Funding
To Be Entered through PLoSONe system and deleted here
Czech Academy of Science visiting fellowship supporting DAC work at AlgaTech (OP)
Canada Research Chair in Phytoplankton Ecophysiology (DAC)
Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC)
New Brunswick Foundation for Innovation (DAC)
Rice Graduate Fellowship (MS)

>>>>

## Detection of *Prochlorococcus* proteins across O~2~ and light niches in the ocean  {.unnumbered}

@@

## *Prochlorococcus marinus* growth responses to photoperiod, PAR, spectral bands,  and O~2~  {.unnumbered}

@@

### MED4 Clade HLI  {.unnumbered}
The GAM model in Figure \@ref(fig:MED4GAM) shows MED4 growth in response to red (A) or blue (B) peak PAR and photoperiod across 2 imposed oxygen concentrations.  Under 250 µM O~2~ MED4 achieved fastest growth rates above peak blue light of ~180 µmol photons m^-2^ s^-1^, and the longest photoperiod of 16, indicated by the 0.69 d^-1^ contour line representing the
90^th^ percentile of maximum achieved growth rate.  Growth decreased with decreasing photoperiod and peak PAR.  Under red light growth was generally slower but the pattern of growth responses to photoperiod and PAR waas similar.  We again note the exclusion of MED4 from growth under 4 h photoperiod. Under 25 µM O~2~ MED4 showed similar growth responses, but was excluded from both 4 and 8 h photoperiods.

@@

# Acknowledgements  {.unnumbered}
Jonah Sheinin assisted with growth of some cultures for protein analyses, while Carlie Barnhill assisted with code for import of multicultivator growth data files.

# Funding  {.unnumbered}
To Be Entered through PLoSONe system and deleted here
Czech Academy of Science visiting fellowship supporting DAC work at AlgaTech (OP)
Canada Research Chair in Phytoplankton Ecophysiology (DAC)
Natural Sciences and Engineering Research Council of Canada, 'Latitude and Light' (DAC)
Canada Foundation for Innovation (DAC)
New Brunswick Foundation for Innovation (DAC)
Rice Graduate Fellowship (MS)
